### 2025-08-14 docs/Homeownership_BankOfMomAndDad.tex
Close #13

\textit{Definition of Transfers:} To measure the transfer receipt rate, I rely on the transfer supplement which asked all parent households whether they gave money, gifts, or loans of \$100 or more to each child in 2012. I follow the literature \citep[e.g.,][]{mcgarry2016dynamic} and treat all transfers as gifts. Since this paper focuses on transfers that (a) relate to housing and (b) are quantitatively meaningful, I ignore transfers below \$500. About 25\% of transfers are below this threshold, and ignoring them increases the conditional mean transfer from \$2,921 to \$3,960 and reduces the transfer receipt rate from 45\% to 22\%.\footnote{These transfer rates are relatively high and exceed those reported by \citealt{feiveson2019lifecycle} using the Survey of Consumer Finances (SCF). The PSID transfer supplement likely captures a broader range of transfers than the SCF, which deliberately focuses on substantial transfers. In addition, the SCF asks about transfers further back in time, increasing the risk of recall error and underreporting.}

>>>>

\textit{Definition of Transfers:} To measure the transfer receipt rate, I rely on the transfer supplement which asked all parents whether they gave money, gifts, or loans of \$100 or more to each child in 2012. I follow the literature \citep[e.g.,][]{mcgarry2016dynamic} and treat all transfers as gifts. I ignore transfers below \$500 to focus on transfers that are quantitatively meaningful for housing. About 25\% of transfers are below this threshold, and ignoring them increases the conditional mean transfer from \$2,921 to \$3,960 and reduces the transfer receipt rate from 45\% to 22\%. It is unsurprising that PSID-based transfer rates exceed those in the SCF \citep[e.g.,][]{feiveson2019lifecycle,sabelhaus2024household}, which focuses on substantial transfers. In the United States, inter-vivos transfers of the magnitudes observed here are far below the federal gift tax limits and are therefore untaxed for both giver and recipient. In 2024, gifts of up to \$18{,}000 per recipient require no filing; gifts above that require a gift-tax return, but tax is owed only if cumulative lifetime gifts and bequests exceed \$13.61 million.
